### 2015-10-28 config/styles.inc.tex
Include initial values
Also quite a bit of pgfplots external trickery/hackery
to make sure the file compiles.

@@

>>>>

\pgfplotsset{compat=newest}

\def\thisDir{.}

\pgfplotsset{tick style={black!30},grid style={black!10}}
\pgfplotsset{every axis legend/.append style={font=\footnotesize}}
\pgfplotsset{every axis label/.append style={font=\footnotesize}}
\pgfplotsset{every tick label/.append style={font=\footnotesize}}
\pgfplotsset{every axis title/.append style={font=\footnotesize}}
\pgfplotsset{every axis post/.style={unbounded coords=jump}}
\pgfplotsset{every axis title/.append style={at={(0.5,0.95)}}}

@@

\definecolor{model}{named}{blue}
\definecolor{truesys}{named}{TangoAluminium5}

\definecolor{sigmalinms}{named}{linms}
\definecolor{sigmaqlogms}{named}{qlogms}
\definecolor{sigmaclogms}{named}{clogms}

\definecolor{biaslinms}{named}{TangoScarletRed1}
\definecolor{biasqlogms}{named}{TangoPlum1}
\definecolor{biasclogms}{named}{TangoSkyBlue1}

\pgfplotsset{linmsgrid/.style={ycomb,color=linms,solid,line width=0.7pt,mark size=1pt,mark=square*,mark options={solid}}}
\pgfplotsset{logmsgrid/.style={ycomb,color=logms,solid,line width=0.7pt,mark size=1pt,mark=*,mark options={solid}}}
\pgfplotsset{clogmsgrid/.style={ycomb,color=clogms,solid,line width=0.7pt,mark size=2pt,mark=x,mark options={solid}}}
\pgfplotsset{plogmsgrid/.style={ycomb,color=plogms,solid,line width=0.7pt,mark size=2pt,mark=triangle,mark options={solid,line width=0.7pt}}}

\pgfplotsset{model/.style={color=model,dashed,line width=1.0pt}}
\pgfplotsset{truesys/.style={color=truesys,line width=1.0pt}}

\newcommand{\linmsmarker}{mark=square,mark options={solid}}
\newcommand{\qlogmsmarker}{mark=triangle,mark options={solid}}
\newcommand{\clogmsmarker}{mark=x,mark size=10pt,mark options={solid}}

\newcommand{\dbamarker}{mark=x       ,mark options={solid}}
\newcommand{\dbbmarker}{mark=o       ,mark options={solid}}
\newcommand{\dbcmarker}{mark=square  ,mark options={solid}}
\newcommand{\dbdmarker}{mark=triangle,mark options={solid}}

\pgfplotsset{sigmalinms/.append style={color=sigmalinms,solid,line width=0.8pt}}
\pgfplotsset{sigmaqlogms/.append style={color=sigmaqlogms,solid,line width=0.8pt}}
\pgfplotsset{sigmaclogms/.append style={color=sigmaclogms,solid,line width=0.8pt}}

\pgfplotsset{biaslinms/.style={color=biaslinms,only marks,mark=x,mark options={solid}}}
\pgfplotsset{biasqlogms/.style={color=biasqlogms,only marks,mark=triangle,mark options={solid,rotate=180}}}
\pgfplotsset{biasclogms/.style={color=biasclogms,only marks,mark=o,mark options={solid}}}

\pgfplotsset{linms/.style={color=linms,solid,line width=0.5pt}}
\pgfplotsset{qlogms/.style={color=qlogms,solid,line width=0.5pt}}
\pgfplotsset{clogms/.style={color=clogms,solid,line width=0.5pt}}

\pgfplotsset{linmsconnect/.style={color=linms,%
                                  solid,
                                  line width=1pt,
                                  mark=square*,
                                  mark size=1pt,
                                  mark options={solid}}}
\pgfplotsset{qlogmsconnect/.style={color=qlogms,%
                                  solid,
                                  line width=1pt,%
                                  mark=*,%
                                  mark size=1pt,
                                  mark options={solid}}}
\pgfplotsset{clogmsconnect/.style={color=clogms,%
                                   solid,
                                   line width=1pt,%
                                   mark=x,%
                                   mark size=1pt,
                                   mark options={solid}}}

\pgfplotsset{dbavar/.style={color=dbacolor,solid,line width=1.0pt}}
\pgfplotsset{dbbvar/.style={color=dbbcolor,solid,line width=1.0pt}}
\pgfplotsset{dbcvar/.style={color=dbccolor,solid,line width=1.0pt}}
\pgfplotsset{dbdvar/.style={color=dbdcolor,solid,line width=1.0pt}}

\pgfplotsset{dbamin/.style={color=dbacolor,dashed,line width=1.0pt}}
\pgfplotsset{dbbmin/.style={color=dbbcolor,dashed,line width=1.0pt}}
\pgfplotsset{dbcmin/.style={color=dbccolor,dashed,line width=1.0pt}}
\pgfplotsset{dbdmin/.style={color=dbdcolor,dashed,line width=1.0pt}}

\pgfplotsset{dbamax/.style={color=dbacolor,solid,line width=1.0pt,mark=x ,mark options={solid}}}
\pgfplotsset{dbbmax/.style={color=dbbcolor,solid,line width=1.0pt,mark=o ,mark options={solid}}}
\pgfplotsset{dbcmax/.style={color=dbccolor,solid,line width=1.0pt,mark=square  ,mark options={solid}}}
\pgfplotsset{dbdmax/.style={color=dbdcolor,solid,line width=1.0pt,mark=triangle,mark options={solid}}}

\definecolor{LPMTrunc}{named}{TangoSkyBlue2}
\definecolor{LPMTruncInit}{named}{TangoSkyBlue2}
\definecolor{RFIR}{named}{TangoScarletRed3}
\definecolor{RFIRInit}{named}{TangoScarletRed1}
\definecolor{existing}{named}{TangoChameleon3}
\definecolor{G0Hat}{named}{TangoOrange2}
\definecolor{GVXI}{named}{G0Hat}
\definecolor{reference}{named}{black}

\definecolor{heuristic}{named}{TangoPlum2}
\definecolor{observed}{named}{TangoOrange3}

\definecolor{best}{named}{TangoAluminium6}

\definecolor{G0HatFill}{named}{TangoOrange1}
\definecolor{GVXIFill}{named}{G0HatFill}
\definecolor{LPMTruncFill}{named}{TangoSkyBlue1}
\definecolor{RFIRFill}{named}{TangoScarletRed1}
\definecolor{existingFill}{named}{TangoChameleon1}
\definecolor{bestFill}{named}{TangoAluminium3}

\definecolor{FRFMean}{named}{TangoPlum3}
\definecolor{FRFSingle}{named}{TangoPlum1}
\definecolor{FRFNoise}{named}{TangoChocolate1}

\pgfplotsset{FRFMean/.style={color=FRFMean,mark=*,mark options={solid},only marks,medsmallmarkers}}
\pgfplotsset{FRFSingle/.style={color=FRFSingle,mark=square*,mark options={solid},only marks,smallmarkers}}
\pgfplotsset{FRFNoise/.style={color=FRFNoise,mark=x,mark options={solid},only marks,smallmarkers}}

\pgfset{number format/1000 sep={\,}}

\pgfplotsset{bandwidth/.style={area style,fill=TangoButter1,draw=TangoButter2,fill opacity=0.5}}
\pgfplotsset{goodestimate/.style={color=TangoChameleon2,line join=round}}
\pgfplotsset{badestimate/.style={color=TangoScarletRed2,solid,line join=round}}
\pgfplotsset{exact/.style={color=black,dashed,line width=0.75pt,line join=round}}

\pgfplotsset{LPMTruncmark/.append style={mark=*,mark options={solid}}}
\pgfplotsset{RFIRmark/.append style={mark=square*,mark options={solid}}}
\pgfplotsset{existingmark/.append style={mark=triangle*,mark options={solid}}}
\pgfplotsset{existingInitmark/.append style={mark=triangle,mark options={solid}}}
\pgfplotsset{LPMTruncInitmark/.append style={mark=o,mark options={solid}}}
\pgfplotsset{RFIRInitmark/.append style={mark=square,mark options={solid}}}
\pgfplotsset{bestmark/.append style={mark=diamond*,mark options={solid}}}
\pgfplotsset{G0Hatmark/.append style={mark=asterisk,mark options={solid}}}

\pgfplotsset{GVXI/.style={color=GVXI,line width=1pt}}
\pgfplotsset{G0Hat/.style={color=G0Hat,line width=1.5pt}}
\pgfplotsset{existing/.style={color=existing}}
\pgfplotsset{LPMTruncInit/.style={color=LPMTruncInit,densely dashed}}
\pgfplotsset{LPMTrunc/.style={color=LPMTrunc}}
\pgfplotsset{RFIRInit/.style={color=RFIRInit,densely dashed}}
\pgfplotsset{RFIR/.style={color=RFIR}}
\pgfplotsset{best/.style={color=best}}

\pgfplotsset{smallmarkers/.append style={mark size=0.75pt}}
\pgfplotsset{medsmallmarkers/.append style={mark size=0.5pt}}
\pgfplotsset{tinymarkers/.append style={mark size=0.25pt}}
\pgfplotsset{extremelytinymarkers/.append style={mark size=0.05pt}}

\tikzset{annotation/.style={align=left,draw=black!0.2,font=\scriptsize,fill=white,fill opacity=0.8}}

%% TABLE STYLES

\pgfplotstableset{
	%zerofill=true,
	after row=[3pt],
	assign column name/.code={%
        \pgfkeyssetvalue{/pgfplots/table/column name}{\multicolumn{1}{c}{\multirow{2}{*}{#1}} }%
    },
	columns/method/.style={string type,column name={\shortstack{\textsc{Method}\\\phantom{0}}}}, 
	columns/contribution/.style={column name={\textsc{Contribution}}},
	columns/P000/.style={column type=r,column name={\shortstack[r]{\textsc{Min.}\\{$0\%$}}}},
	columns/P025/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$25\%$}}}},
	columns/P050/.style={column type=r,column name={\shortstack[r]{\textsc{Median}\\{$50\%$}}}},
	columns/P075/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$75\%$ }}}},
	columns/P100/.style={column type=r,column name={\shortstack[r]{\textsc{Max.}\\{$100\%$}}}},
	columns/contribution/.style={column name={\shortstack[r]{\textsc{Contribution}\\ \vphantom{0}}},
	postproc cell content/.append code={
            %\ifnum1=\pgfplotstablepartno
                \pgfkeysalso{@cell content/.add={}{\%}}%
            %\fi
        },
	},
	every head row/.style={before row=\toprule, after row={\\\midrule}},
    every last row/.style={after row=\bottomrule}
}
